Computing in the Field of Rationals

### 2012-06-26 rational_ext.tex
_

\begin{definition}[{{c1  = c2}}]
We say {{c1 = c2}} if {{c1:b1<->b2}} and {{c2:b1<->b2}} and for all
{{v1:b}}, we have {{c1 v1 |--> v2}} iff {{c2 v1 |--> v2}} and {{v2:b2}}.
\end{definition}

@@

\begin{definition}[c1 = c2]
We say that {{c1 = c2}}, for combinators {{c1:b1<->b2}} and
{{c2:b1<->b2}} iff they denote the same relation. Equivalently,
{{forall v:b1. eval(c1, v) = eval(c2, v)}}.
\end{definition}

>>>>

\begin{definition}[ {{c1  = c2}} ]
We say {{c1 = c2}} if {{c1:b1<->b2}} and {{c2:b1<->b2}} and for all
{{v1:b}}, we have {{c1 v1 |--> v2}} iff {{c2 v1 |--> v2}} and {{v2:b2}}.
\end{definition}

@@

\begin{definition}[{{c1 = c2}}]
We say that {{c1 = c2}}, for combinators {{c1:b1<->b2}} and
{{c2:b1<->b2}} iff they denote the same relation. Equivalently,
{{forall v:b1. eval(c1, v) = eval(c2, v)}}.
\end{definition}
